Natural variations in water discharge quantity have an inconsistent impact on sediment transport capacity in subglacial channels

### 2023-10-09 Delaneyetal2023b.tex
table A1

\appendix
\section{Table of variables, parameters and constants}
\begin{table}[h]
  \centering
  \caption{Variables, parameters, and constants used in this work.
    Where two values are given, the first refers to  \alpine{}, a case from Fieschergletscher, and the second to a glacier marginal to the \icesheet{} a case from Leverett Glacier}
  \begin{tabular}{ l  c  c c }
    Name &Symbol&  Value&Units \\ \hline
    \textbf{Variables}  & & & \\
    Water discharge  & $Q$& & $\mathrm{m^{3}\,s^{-1}}$ \\
    Water velocity (glacier, subaerial)  & $v_g,\,v_{f}$& & $\mathrm{m\,s^{-1}}$ \\
    Channel wetted area (glacier, subaerial) &  $S_g, S_f$& & $\mathrm{m^2}$     \\
    Channel depth (subaerial) & &$H$& $\mathrm{m}$\\
    Hydraulic diameter &$D_h$&&$\mathrm{m}$\\
    Width of channel floor (glacial, subaerial) & $w_g,w_f$&  & $\mathrm{m}$     \\
    Hydraulic head &$\Delta h$&& $\mathrm{m}$\\
    Hydraulic gradient &$\Psi=\frac{\Delta h}{l}$&& $\mathrm{m\, m^{-1}}$\\

    Shear stress (glacier, subaerial) & $\tau_g,\,\tau_f$&& $\mathrm{Pa \, m^{-2}}$ \\
    Width-integrated shear stress (glacier, subaerial) & $\tau_{tg},\, \tau_{tf}$&& $\mathrm{Pa \, m^{-1}}$ \\
    Stream power & $\Omega$ && $\mathrm{ kg \, m\, s^{-3}}$ \\

@@

Table~\ref{tab:Qs2} shows how the proxy $w\tau$ as well as $Q_s$ of the MPM, EH and Bagnold sediment transport formulas scale with respect to $Q$, $\Psi$ or $S$ for the three different regimes and for different $\alpha$.
Remarkably, the Bagnold formula has a negative exponent for $f$ in all but the pipe-flow regime, which seems rather unexpected.
The total transport formula EH gives a slightly stronger dependence on all variables as should be expected due to the larger exponent on $\tau$ of $\frac{5}{2}$ versus  $\frac{3}{2}$  for the others.
Albeit, the sediment transport response in pipe-flow for the Bagnold case is close to EH.
Conversely, the sediment transport proxy $w_g\,\tau_{g}, w_f\,\tau_{f}$ used within this publication scales only as $Q^2$ for pipe-flow, whereas the others scale at least with $Q^3$.
The exponent for the width scaling $\alpha$ only impacts relationship between sediment transport and water discharge in the EH relation in any meaningful way.
However, for the value of $\alpha$ around $\frac{1}{2}$ (a value appropriate for most streams), the exponent on $Q$ for EH is only slightly above what the other transport relations give.

>>>>

\appendix
\section{Table of variables, parameters and constants}
\begin{table}[h]
  \centering
  \caption{Variables, parameters, and constants used in this work.
    Where two values are given, the first refers to  \alpine{}, a case from Fieschergletscher, and the second to a glacier marginal to the \icesheet{} a case from Leverett Glacier}
  \begin{tabular}{ l  c  c c }
    Name &Symbol&  Value&Units \\ \hline
    \textbf{Variables}  & & & \\
    Water discharge  & $Q$& & $\mathrm{m^{3}\,s^{-1}}$ \\
    Water velocity (glacier, subaerial)  & $v$, ($v_g,\,v_{f}$)& & $\mathrm{m\,s^{-1}}$ \\
    Channel wetted area (glacier, subaerial) &  $S_g, S_f$& & $\mathrm{m^2}$     \\
    Channel depth (subaerial) & $H$&& $\mathrm{m}$\\
    Hydraulic diameter &$D_h$&&$\mathrm{m}$\\
    Width of channel floor (glacial, subaerial) & $w$, ($w_g,w_f$)&  & $\mathrm{m}$     \\
    Hydraulic head &$\Delta h$&& $\mathrm{m}$\\
    Hydraulic gradient &$\Psi=\frac{\Delta h}{l}$&& $\mathrm{m\, m^{-1}}$\\

    Shear stress (glacier, subaerial) & $\tau$, ($\tau_g,\,\tau_f$) && $\mathrm{Pa \, m^{-2}}$ \\
    Width-integrated shear stress (glacier, subaerial) \mauro{get rid of this} & $\tau_{tg},\, \tau_{tf}$&& $\mathrm{Pa \, m^{-1}}$\\
    Stream power & $\Omega$ && $\mathrm{ kg \, m\, s^{-3}}$ \\

@@

Table~\ref{tab:Qs2} shows how the proxy $w\tau$ as well as $Q_s$ of the MPM, EH and Bagnold sediment transport formulas scale with respect to $Q$, $\Psi$ or $S$ for the three different regimes and for different $\alpha$.
Remarkably, the Bagnold formula has a negative exponent for $f$ in all but the pipe-flow regime, which seems rather unexpected.
The total transport formula EH gives a slightly stronger dependence on all variables as should be expected due to the larger exponent on $\tau$ of $\frac{5}{2}$ versus  $\frac{3}{2}$  for the others.
Albeit, the sediment transport response in pipe-flow for the Bagnold case is close to EH.
Conversely, the sediment transport proxies $w_g\,\tau_g$ \& $w_f\,\tau_f$ used within this publication scale only as $Q^2$ for pipe-flow, whereas the transport scales at least with $Q^3$.
The exponent for the width scaling $\alpha$ only impacts relationship between sediment transport and water discharge in the EH relation in any meaningful way.
However, for the value of $\alpha$ around $\frac{1}{2}$ (a value appropriate for most streams), the exponent on $Q$ for EH is only slightly above what the other transport relations give.
